A meta-analysis of mental rotation ability in the first years of life

### 2022-04-21 code/analysis.Rmd
Add forest plot

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)

@@

# Directory paths
data_dir <- here("data")

@@

>>>>

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)
library(tidybayes)

@@

# Directory paths
data_dir <- here("data")
figures_dir <- here("results/figures")

@@

```{r, fig2}
# Forest plot inputs
level <- 0.05
ndraws <- 1000
dat_plot <- dat_both_mixed
res_plot <- res_ml
res_plot_brm <- res_brm

# Helper function for printing confidence intervals
print_num <- function(x) format(round(x, 2), trim = TRUE, nsmall = 2)
print_ci <- function(est, lb, ub) {
  paste0(print_num(est), " [", print_num(lb), ", ", print_num(ub), "]")
}

# Get draws from the Bayesian posterior distribution
draws <- epred_draws(res_brm, dat_plot, ndraws = ndraws)
meta_draws <- spread_draws(res_brm, b_Intercept, ndraws = ndraws) %>%
  mutate(article = "Three-level model", experiment = "zzz") # For the last line

# Create forest plot
dat_plot %>%
  # Compute frequentist confidence intervals
  mutate(
    ci_lb = gi - qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(level / 2, lower.tail = FALSE) * sqrt(vi),
    fontface = "plain" # For study labels and confidence interval
  ) %>%
  # Add meta-analytic effect size + CI
  bind_rows(list(
    article = "Three-level model",
    group = "",
    experiment = "zzz", # Just so it's displayed as the last line
    gi = res_plot$b,
    ci_lb = res_plot$ci.lb,
    ci_ub = res_plot$ci.ub,
    fontface = "bold"
  )) %>%
  # Format effect size + CI for printing them on the plot
  mutate(ci_print = print_ci(gi, ci_lb, ci_ub)) %>%
  # Reverse order of experiments so they are plotted alphabetically
  mutate(experiment = forcats::fct_rev(factor(experiment))) %>%
  arrange(experiment) %>%
  # Show article labels only for the first experiment per article
  mutate(
    article = if_else(article == lead(article, default = ""), "", article)
  ) %>%
  # Prepare plot
  ggplot(aes(x = gi, y = experiment)) +
  geom_vline(xintercept = seq(-1, 2, 1), size = 0.8, color = "grey90") +
  geom_vline(xintercept = seq(-1.5, 2.5, 1), size = 0.4, color = "grey90") +
  # Add article and group labels as text to the left
  geom_text(aes(x = -5.6, label = article, fontface = fontface), hjust = 0) +
  geom_text(aes(x = -3.1, label = group, fontface = fontface), hjust = 0) +
  # Add experiment specific effect size + CI as text to the right
  geom_text(aes(x = 4.4, label = ci_print, fontface = fontface), hjust = 1) +
  # Add Bayesian highest posterior density interval in the background
  stat_interval(aes(x = .epred), draws, point_interval = "mean_hdi") +
  stat_interval(aes(x = b_Intercept), meta_draws, point_interval = "mean_hdi") +
  # Add study specific effect size + CIs on top
  geom_errorbar(aes(xmin = ci_lb, xmax = ci_ub)) +
  geom_point(aes(size = ni), shape = 15) + # Or (1 / vi)?
  # Add meta-analytic effect size as a line
  annotate("segment", x = res_plot$b, xend = res_plot$b, y = 0.7, yend = 1.3) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(breaks = seq(-1.5, 2.5, 0.5)) +
  scale_color_grey(
    start = 0.9, end = 0.6,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "Bayesian HPDI"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.584),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
ggsave(here(figures_dir, "forest.pdf"), width = 9, height = 13)
```
